\chapter[Optical color MIMO: Impact of visual perception on CSK]{Impact of visual perception on CSK}
\label{chapter:mimoColor}
\thispagestyle{myheadings}
As seen in previous chapter, imaging receivers have the potential to provide significant performance gains for a spatial MIMO OWC system. To incorporate these in portable devices, they must address challenges of being low powered, have fast sampling rates while incorporating optics, sensor and electronics in a small form factor.

%This chapter explores the color dimension to establish an optical MIMO channel. It investigates CSK as specified in IEEE 80.15.7 standard PHY  \rmnum{3}. The standard specifies a simplified linear system model for CSK. The human visual perception model is non--linear and needs to be considered while providing illumination. Thus a non--linear CSK model is investigated for different color band combinations. LSNR metric is introduced to make fair performance comparisons between different modulation techniques operating at different average radiant flux, but same average luminous flux levels. MM then further explores color dimension by using multiple sets of LEDs to transmit information over metamerically equivalent SPDs \cite{but12a}.
The IEEE 802.15.7 standard defines specifications for short--range OWC using visible light. The standard specifies CSK as the preferred modulation scheme for indoor OWC while simultaneously providing illumination. This chapter considers the performance of $M$-ary CSK under the linear system model as specified in the standard. In light of illumination requirements, human eye's optical perception introduces unique non-linearities in the CSK signaling chain. It is shown that these non-linearities introduce performance penalties of more than 15 dB, 10 dB, and 5 dB for $M$ = 4, 8, and 16 CSK respectively. A new metric called LSNR is also introduced to fairly compare performance of any two OWC signaling schemes operating at a user defined illumination intensity level and is used to compare performance of $M$-ary CSK implemented with different colored sources. At a target BER $\leq 10^{-3}$, simulation results indicate that clipping negative receiver output does not have an impact on $M$-ary CSK performance.

% -------------------------------------
% SECTION: IEEE 802.15.7
% -------------------------------------
\input{_MIMOColor/ieeestd}

% -------------------------------------
% SECTION: CSK
% -------------------------------------
\input{_MIMOColor/csk}

% -------------------------------------
% SECTION: Metameric Modulation
% -------------------------------------
\input{_MIMOColor/metameric}