\addcontentsline{toc}{chapter}{Resume}

\thispagestyle{empty}

\begin{center}
%{\LARGE {\bf CURRICULUM VITAE}}\\
\cvtitle{Resume}\\
\vspace{0.3in}
%{\large {\bf Pankil M Butala}}
\cvname{Pankil M. Butala}\\
pankil.butala@gmail.com
\end{center}
\vspace{0.1in}
%Basically, this needs to be worked out by each individual, however the same format, margins, typeface, and type size must be used as in the rest of the dissertation. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvheadi{Education}
\vspace{0.05in}\\
%\cvheadii{} \hfill \cvdate{}\\
%\cvheadiii{}
%\begin{itemize}[noitemsep,topsep=0em,leftmargin=2em]
	%\item 
%\end{itemize}
\cvheadii{Boston University, Boston, MA} \hfill \cvdate{2015}\\
\cvheadiii{Doctor of Philosophy Candidate, Electrical and Computer Engineering}
\begin{itemize}[noitemsep,topsep=0.25em,leftmargin=1.25em]
	\item Ph.D. Dissertation: Optical MIMO communication systems under illumination constraints.
	\item Developed low complexity spectrally efficient MIMO OFDM signaling schemes.
\end{itemize}
\vspace{0.05in}
\cvheadii{University of California, Los Angeles, CA}  \hfill \cvdate{2007}\\
\cvheadiii{Master of Science, Biomedical Engineering}
\begin{itemize}[noitemsep,topsep=0.25em,leftmargin=1.25em]
	\item Designed multi-tap FIR/IIR digital filters.
	\item Developed java based GUI to parse DICOM images.
\end{itemize}
\vspace{0.05in}
\cvheadii{University of Mumbai, Mumbai, India}  \hfill \cvdate{2006}\\
\cvheadiii{Bachelor of Engineering, Biomedical Engineering}
\newline\newline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvheadi{Work Experience}
\vspace{0.05in}\\
\cvheadii{Multimedia Communication Laboratory \& Smart Lighting ERC, Boston University, Boston, MA}\hfill \cvdate{2011 -- 2015}\\
\cvheadiii{Research Assistant}
\begin{itemize}[noitemsep,topsep=0.25em,leftmargin=1.25em]
	\item Designed Xilinx FPGA based optical wireless 4x4 MIMO system with an imaging receiver and implementing OFDM variant as modulation at PHY.
	\item Developed a wireless, networked color sensor platform (CuSP) to deploy in smart spaces.
	\item Designed an iOS app and wireless, networked inertial sensors (FAM) for monitoring, detection and real--time classification of functional activity.
\end{itemize}
\cvheadii{Advanced Analytical Technologies, Inc., Ames, IA} \hfill \cvdate{2009 -- 2010}\\
\cvheadiii{Software Engineer}
\begin{itemize}[noitemsep,topsep=0.25em,leftmargin=1.25em]
	\item Developed GUI data analysis and controller software in C\# for analytical laboratory instruments.
	\item Implemented real time control, digital signal processing, pattern search and match algorithms.
\end{itemize}
\cvheadii{Enova Systems, Inc./HE-ITC, Torrance, CA} \hfill \cvdate{2007 -- 2009}\\
\cvheadiii{Software Engineer}
\begin{itemize}[noitemsep,topsep=0.25em,leftmargin=1.25em]
	\item Developed embedded code in C/C++ for hybrid vehicle motor drive control modules.
	\item Developed an in house UI tool to obtain real time system diagnostic data.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvheadi{Publications}
\begin{itemize}[topsep=0.5em,leftmargin=1.25em]
	\item Trace-orthogonal PPM - Space time block coding under rate constraints for visible light communication \hfill 2015 \\
	Journal of Lighwave Technology, (33), 2, pp. 481-494\\
	M. Biagi, A. M. Vegni, S. Pergoloni, \textbf{P. Butala} and T.D.C. Little
	\item Multi-wavelength visible light communication system design \hfill 2014\\ 
	IEEE Globecom Workshop on OWC\\
	\textbf{P. Butala},  H. Elgala, P. Z-Ha and T.D.C. Little
	\item Sample indexed spatial orthogonal frequency division multiplexing \hfill 2014\\ 
	Chinese Optics Letters, (12), 9, pp. 090602\\
	\textbf{P. Butala}, H. Elgala and T.D.C. Little
	\item Performance of optical spatial modulation and spatial multiplexing with imaging receiver \hfill 2014\\
	IEEE Wireless Communications and Networking Conference\\
	\textbf{P. Butala}, H. Elgala and T.D.C. Little
	\item SVD-VLC: A novel capacity maximizing VLC MIMO system architecture under illumination constraints \hfill 2013\\
	IEEE Globecom Workshop on OWC\\
	\textbf{P. Butala}, H. Elgala and T.D.C. Little
	\item Metameric modulation for diffuse visible light communications with constant ambient lighting \hfill 2012\\
	International Workshop on OWC\\
	\textbf{P. Butala}, J. Chau and T.D.C. Little
	\item Monitoring walking and cycling of middle-aged to older community dwellers using wireless wearable accelerometers \hfill 2012\\
	Annual International Conference of the IEEE EMBC\\
	Y. Zhang, K. Beenakker, \textbf{P. Butala}, C. Lin, T.D.C. Little, A. Maier, M. Stijntjes, R. Vartanian and R. Wagenaar
	\item Wireless system for monitoring and real time classification of functional activity\\ \text{ }\hfill 2012\\
	Fourth International Conference on COMSNETS\\
	\textbf{P. Butala}, Y. Zhang, T.D.C. Little and R. Wagenaar
	%\item a \hfill 201\\
	%\\
	%\textbf{P. Butala}
\end{itemize}
%\newline\newline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvheadi{Awards and Leadership}\\
%\begin{tabular*}{\textwidth}{@{\extracolsep{\fill} } l l r }
%President & SLC, Smart Lighting ERC & 2014 -- 2015\\
%Dean's Fellowship & Boston University & 2010 -- 2011 \\
%\end{tabular*}
